---
title: "QC lipidyzer report"
author: "Rico Derks"
date: '`r Sys.Date()`'
output: 
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
params:
  myfiles: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(readxl)
library(purrr)

myfiles <- params$myfiles

sheet_names <- c("Lipid Species Concentrations",
                 "Lipid Species Composition",
                 "Lipid Class Concentration",
                 "Lipid Class Composition",
                 "Fatty Acid Concentration",
                 "Fatty Acid Composition")
```

# Introduction

This report will give an overview of the QC samples from a lipidyzer study.

```{r read_all_data}
df <- data_frame(datapath = rep(myfiles$datapath, each = length(sheet_names)), 
                 sheet_names = rep(sheet_names, nrow(myfiles)))
df <- df %>%
  mutate(batch = rep(seq(1, length(unique(datapath))), each = length(unique(sheet_names)))) %>%
  mutate(batch_bar = rep(c(1, 2), each = length(unique(sheet_names)), length.out = length(unique(sheet_names)) * length(unique(datapath)))) %>%
  mutate(data = map2(.x = datapath,
                     .y = sheet_names,
                     .f = ~ read_excel(path = .x,
                                       sheet = .y,
                                       col_names = TRUE,
                                       na = "."))) %>%
  mutate(data = map2(.x = data,
                     .y = batch,
                     .f = ~ mutate(.x, batch = .y))) %>%
  mutate(data = map2(.x = data,
                     .y = batch_bar,
                     .f = ~ mutate(.x, batch_bar = .y)))
```

# Lipid classes

## Concentration

```{r class_concentration}
# filter out only what I want
class <- df %>%
  filter(sheet_names == sheet_names[3]) %>%
  select(data) %>%
  unnest %>%
  filter(grepl(Name, pattern = "QC-[0-9]*")) %>%
  gather(lipid, value, -Name, -batch, -batch_bar)  %>%
  mutate(Name = factor(Name, levels = unique(Name)),
         lipid = as.factor(lipid),
         batch = as.factor(batch),
         batch_bar = as.factor(batch_bar))
```

```{r class_concentration_table}
class  %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid class", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r class_concentration_line}
class %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration") +
  facet_wrap(~ lipid, ncol = 3, scales = "free_y")
```

## Composition

```{r class_composition}
# filter out only what I want
class <- df %>%
  filter(sheet_names == sheet_names[4]) %>%
  select(data) %>%
  unnest %>%
  filter(grepl(Name, pattern = "QC-[0-9]*")) %>%
  gather(lipid, value, -Name, -batch, -batch_bar)  %>%
  mutate(Name = factor(Name, levels = unique(Name)),
         lipid = as.factor(lipid),
         batch = as.factor(batch),
         batch_bar = as.factor(batch_bar))
```

```{r class_composition_table}
class  %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid class", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r class_composition_line}
class %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition") +
  facet_wrap(~ lipid, ncol = 3, scales = "free_y")
```

# Lipid species

## Concentration

```{r species_concentration}
# filter out only what I want
species <- df %>%
  filter(sheet_names == sheet_names[1]) %>%    # select the lipid species concentration sheet
  select(data) %>%
  unnest %>%
  select(-batch_bar) %>%    # remove the batch_bar column
  filter(grepl(Name, pattern = "QC-[0-9]*")) %>%
  gather(lipid, value, -Name, -batch)  %>%
  mutate(lipid_class = as.factor(gsub(x = lipid,
                                      pattern = "[\\(]{0,1}[0-9.].*",
                                      replacement = ""))) %>%
  mutate(Name = factor(Name, levels = unique(Name)),
         lipid = factor(lipid, levels = unique(lipid)),
         batch = as.factor(batch))
```

### Cholesterol esters

```{r species_concentration_table_CE, warning=FALSE}
species  %>%
  filter(lipid_class == "CE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_concentration_line_CE, warning=FALSE}
species %>%
  filter(lipid_class == "CE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Diacylglycerols

```{r species_concentration_table_DAG, warning=FALSE}
species  %>%
  filter(lipid_class == "DAG") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_concentration_line_DAG, warning=FALSE}
species %>%
  filter(lipid_class == "DAG") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Free fatty acids

```{r species_concentration_table_FFA, warning=FALSE}
species  %>%
  filter(lipid_class == "FFA") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_concentration_line_FFA, warning=FALSE}
species %>%
  filter(lipid_class == "FFA") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Lysophosphatidylcholines

```{r species_concentration_table_LPC, warning=FALSE}
species  %>%
  filter(lipid_class == "LPC") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_concentration_line_LPC, warning=FALSE}
species %>%
  filter(lipid_class == "LPC") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Lysophosphatidylethanolamine

```{r species_concentration_table_LPE, warning=FALSE}
species  %>%
  filter(lipid_class == "LPE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_concentration_line_LPE, warning=FALSE}
species %>%
  filter(lipid_class == "LPE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Phosphatidylcholines

```{r species_concentration_table_PC, warning=FALSE}
species  %>%
  filter(lipid_class == "PC") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_concentration_line_PC, warning=FALSE}
species %>%
  filter(lipid_class == "PC") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Phosphatidylethanolamines

```{r species_concentration_table_PE, warning=FALSE}
species  %>%
  filter(lipid_class == "PE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_concentration_line_PE, warning=FALSE}
species %>%
  filter(lipid_class == "PE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Sphingomyelins

```{r species_concentration_table_SM, warning=FALSE}
species  %>%
  filter(lipid_class == "SM") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_concentration_line_SM, warning=FALSE}
species %>%
  filter(lipid_class == "SM") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Triacylglycerols

```{r species_concentration_table_TAG, warning=FALSE}
species  %>%
  filter(lipid_class == "TAG") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_concentration_line_TAG, warning=FALSE}
species %>%
  filter(lipid_class == "TAG") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

## Composition

```{r species_composition}
# filter out only what I want
species <- df %>%
  filter(sheet_names == sheet_names[2]) %>%    # select the lipid species composition sheet
  select(data) %>%
  unnest %>%
  select(-batch_bar) %>%    # remove the batch_bar column
  filter(grepl(Name, pattern = "QC-[0-9]*")) %>%
  gather(lipid, value, -Name, -batch)  %>%
  mutate(lipid_class = as.factor(gsub(x = lipid,
                                      pattern = "[\\(]{0,1}[0-9.].*",
                                      replacement = ""))) %>%
  mutate(Name = factor(Name, levels = unique(Name)),
         lipid = factor(lipid, levels = unique(lipid)),
         batch = as.factor(batch))
```

### Cholesterol esters

```{r species_composition_table_CE, warning=FALSE}
species  %>%
  filter(lipid_class == "CE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_composition_line_CE, warning=FALSE}
species %>%
  filter(lipid_class == "CE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Diacylglycerols

```{r species_composition_table_DAG, warning=FALSE}
species  %>%
  filter(lipid_class == "DAG") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_composition_line_DAG, warning=FALSE}
species %>%
  filter(lipid_class == "DAG") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Free fatty acids

```{r species_composition_table_FFA, warning=FALSE}
species  %>%
  filter(lipid_class == "FFA") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_composition_line_FFA, warning=FALSE}
species %>%
  filter(lipid_class == "FFA") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Lysophosphatidylcholines

```{r species_composition_table_LPC, warning=FALSE}
species  %>%
  filter(lipid_class == "LPC") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_composition_line_LPC, warning=FALSE}
species %>%
  filter(lipid_class == "LPC") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Lysophosphatidylethanolamine

```{r species_composition_table_LPE, warning=FALSE}
species  %>%
  filter(lipid_class == "LPE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_composition_line_LPE, warning=FALSE}
species %>%
  filter(lipid_class == "LPE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Phosphatidylcholines

```{r species_composition_table_PC, warning=FALSE}
species  %>%
  filter(lipid_class == "PC") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_composition_line_PC, warning=FALSE}
species %>%
  filter(lipid_class == "PC") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Phosphatidylethanolamines

```{r species_composition_table_PE, warning=FALSE}
species  %>%
  filter(lipid_class == "PE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_composition_line_PE, warning=FALSE}
species %>%
  filter(lipid_class == "PE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Sphingomyelins

```{r species_composition_table_SM, warning=FALSE}
species  %>%
  filter(lipid_class == "SM") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_composition_line_SM, warning=FALSE}
species %>%
  filter(lipid_class == "SM") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Triacylglycerols

```{r species_composition_table_TAG, warning=FALSE}
species  %>%
  filter(lipid_class == "TAG") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("Lipid species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r species_composition_line_TAG, warning=FALSE}
species %>%
  filter(lipid_class == "TAG") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

# Fatty acid species

## Concentration

```{r fa_concentration}
# filter out only what I want
fa <- df %>%
  filter(sheet_names == sheet_names[5]) %>%    # select the lipid fa concentration sheet
  select(data) %>%
  unnest %>%
  select(-batch_bar) %>%    # remove the batch_bar column
  filter(grepl(Name, pattern = "QC-[0-9]*")) %>%
  gather(lipid, value, -Name, -batch)  %>%
  mutate(lipid_class = as.factor(gsub(x = lipid,
                                      pattern = "[\\(](FA).*",
                                      replacement = ""))) %>%
  mutate(Name = factor(Name, levels = unique(Name)),
         lipid = factor(lipid, levels = unique(lipid)),
         batch = as.factor(batch))
```

### Cholesterol esters

```{r fa_concentration_table_CE, warning=FALSE}
fa  %>%
  filter(lipid_class == "CE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_concentration_line_CE, warning=FALSE}
fa %>%
  filter(lipid_class == "CE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Diacylglycerols

```{r fa_concentration_table_DAG, warning=FALSE}
fa  %>%
  filter(lipid_class == "DAG") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_concentration_line_DAG, warning=FALSE}
fa %>%
  filter(lipid_class == "DAG") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Free fatty acids

```{r fa_concentration_table_FFA, warning=FALSE}
fa  %>%
  filter(lipid_class == "FFA") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_concentration_line_FFA, warning=FALSE}
fa %>%
  filter(lipid_class == "FFA") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Lysophosphatidylcholines

```{r fa_concentration_table_LPC, warning=FALSE}
fa  %>%
  filter(lipid_class == "LPC") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_concentration_line_LPC, warning=FALSE}
fa %>%
  filter(lipid_class == "LPC") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Lysophosphatidylethanolamine

```{r fa_concentration_table_LPE, warning=FALSE}
fa  %>%
  filter(lipid_class == "LPE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_concentration_line_LPE, warning=FALSE}
fa %>%
  filter(lipid_class == "LPE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Phosphatidylcholines

```{r fa_concentration_table_PC, warning=FALSE}
fa  %>%
  filter(lipid_class == "PC") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_concentration_line_PC, warning=FALSE}
fa %>%
  filter(lipid_class == "PC") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Phosphatidylethanolamines

```{r fa_concentration_table_PE, warning=FALSE}
fa  %>%
  filter(lipid_class == "PE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_concentration_line_PE, warning=FALSE}
fa %>%
  filter(lipid_class == "PE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Sphingomyelins

```{r fa_concentration_table_SM, warning=FALSE}
fa  %>%
  filter(lipid_class == "SM") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_concentration_line_SM, warning=FALSE}
fa %>%
  filter(lipid_class == "SM") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

### Triacylglycerols

```{r fa_concentration_table_TAG, warning=FALSE}
fa  %>%
  filter(lipid_class == "TAG") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_concentration_line_TAG, warning=FALSE}
fa %>%
  filter(lipid_class == "TAG") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Concentration")
```

## Composition

```{r fa_composition}
# filter out only what I want
fa <- df %>%
  filter(sheet_names == sheet_names[6]) %>%    # select the lipid fa composition sheet
  select(data) %>%
  unnest %>%
  select(-batch_bar) %>%    # remove the batch_bar column
  filter(grepl(Name, pattern = "QC-[0-9]*")) %>%
  gather(lipid, value, -Name, -batch)  %>%
  mutate(lipid_class = as.factor(gsub(x = lipid,
                                      pattern = "[\\(](FA).*",
                                      replacement = ""))) %>%
  mutate(Name = factor(Name, levels = unique(Name)),
         lipid = factor(lipid, levels = unique(lipid)),
         batch = as.factor(batch))
```

### Cholesterol esters

```{r fa_composition_table_CE, warning=FALSE}
fa  %>%
  filter(lipid_class == "CE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_composition_line_CE, warning=FALSE}
fa %>%
  filter(lipid_class == "CE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Diacylglycerols

```{r fa_composition_table_DAG, warning=FALSE}
fa  %>%
  filter(lipid_class == "DAG") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_composition_line_DAG, warning=FALSE}
fa %>%
  filter(lipid_class == "DAG") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Free fatty acids

```{r fa_composition_table_FFA, warning=FALSE}
fa  %>%
  filter(lipid_class == "FFA") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_composition_line_FFA, warning=FALSE}
fa %>%
  filter(lipid_class == "FFA") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Lysophosphatidylcholines

```{r fa_composition_table_LPC, warning=FALSE}
fa  %>%
  filter(lipid_class == "LPC") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_composition_line_LPC, warning=FALSE}
fa %>%
  filter(lipid_class == "LPC") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Lysophosphatidylethanolamine

```{r fa_composition_table_LPE, warning=FALSE}
fa  %>%
  filter(lipid_class == "LPE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_composition_line_LPE, warning=FALSE}
fa %>%
  filter(lipid_class == "LPE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Phosphatidylcholines

```{r fa_composition_table_PC, warning=FALSE}
fa  %>%
  filter(lipid_class == "PC") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_composition_line_PC, warning=FALSE}
fa %>%
  filter(lipid_class == "PC") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Phosphatidylethanolamines

```{r fa_composition_table_PE, warning=FALSE}
fa  %>%
  filter(lipid_class == "PE") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_composition_line_PE, warning=FALSE}
fa %>%
  filter(lipid_class == "PE") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Sphingomyelins

```{r fa_composition_table_SM, warning=FALSE}
fa  %>%
  filter(lipid_class == "SM") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_composition_line_SM, warning=FALSE}
fa %>%
  filter(lipid_class == "SM") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```

### Triacylglycerols

```{r fa_composition_table_TAG, warning=FALSE}
fa  %>%
  filter(lipid_class == "TAG") %>%
  select(lipid, value, Name) %>%
  group_by(lipid) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            stdev = sd(value, na.rm = TRUE),
            RSD = stdev / mean * 100) %>%
  DT::datatable(colnames = c("FA species", "Mean", "St.dev.", "RSD [%]"),
                options = list(dom = "pt"), selection = "none") %>%             # remove the search field
  formatRound(columns = c("mean", "stdev", "RSD"), digits = 2)
```

```{r fa_composition_line_TAG, warning=FALSE}
fa %>%
  filter(lipid_class == "TAG") %>%
  select(lipid, value, Name, batch) %>%
  ggplot +
  geom_point(aes(x = Name,
                 y = value,
                 color = lipid,
                 shape = batch),
             size = 3) +
  geom_path(aes(x = Name,
                y = value,
                color = lipid,
                group = lipid)) +
  guides(color = "none",
         shape = guide_legend(title = "Batch")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("QC sample ID") +
  ylab("Composition")
```